Scaling through abstractions – high-performance vectorial wave simulations for seismic inversion with Devito

### 2020-04-21 paper.tex
final version

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Devito for large scale elastic modelling and anisotropic inversion.},
            colorlinks=true,
            citecolor=black,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

\title{Scaling through abstraction – high-performance vectorial wave simulations for seismic inversion with Devito}

\author{
\IEEEauthorblockN{1\textsuperscript{st} Mathias Louboutin}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Antlanta, GA \\
mlouboutin3@gatech.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Fabio Luporini}
\IEEEauthorblockA{\textit{Devito Codes}\\
London, UK \\
fabio@devitocodes.com}
\and
\IEEEauthorblockN{3\textsuperscript{th} Rhodri Nelson}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
rhodri.nelson@imperial.ac.uk}
\and
\IEEEauthorblockN{4\textsuperscript{rd} Philipp Witte}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Atlanta, GA \\
pwitte3@gatech.edu}
\and
\IEEEauthorblockN{5\textsuperscript{th} George Bisbas}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
g.bisbas18@imperial.ac.uk}
\and
\IEEEauthorblockN{6\textsuperscript{th} Jan Thorbecke}
\IEEEauthorblockA{\textit{TU-Delft}\\
Delft, NL \\
J.W.Thorbecke@tudelft.nl}
\and
\IEEEauthorblockN{7\textsuperscript{th} Felix J. Herrmann}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Atlanta, GA\\
felix.herrmann@gatech.edu}
\and
\IEEEauthorblockN{8\textsuperscript{th} Gerard J. Gorman}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
g.gorman@imperial.ac.uk}
}

>>>>

\documentclass[10pt, conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Scaling through abstractions – high-performance vectorial wave simulations for seismic inversion with Devito},
            colorlinks=true,
            citecolor=black,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

\title{Scaling through abstractions – high-performance vectorial wave simulations for seismic inversion with Devito}

\author{
\IEEEauthorblockN{1\textsuperscript{st} Mathias Louboutin}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Antlanta, GA \\
mlouboutin3@gatech.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Fabio Luporini}
\IEEEauthorblockA{\textit{Devito Codes}\\
London, UK \\
fabio@devitocodes.com}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Rhodri Nelson}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
rhodri.nelson@imperial.ac.uk}
\and
\IEEEauthorblockN{4\textsuperscript{th} Philipp Witte}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Atlanta, GA \\
pwitte3@gatech.edu}
\and
\IEEEauthorblockN{5\textsuperscript{th} George Bisbas}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
g.bisbas18@imperial.ac.uk}
\and
\IEEEauthorblockN{6\textsuperscript{th} Jan Thorbecke}
\IEEEauthorblockA{\textit{TU-Delft}\\
Delft, NL \\
J.W.Thorbecke@tudelft.nl}
\and
\IEEEauthorblockN{7\textsuperscript{th} Felix J. Herrmann}
\IEEEauthorblockA{\textit{Georgia Institute of Technology}\\
Atlanta, GA\\
felix.herrmann@gatech.edu}
\and
\IEEEauthorblockN{8\textsuperscript{th} Gerard J. Gorman}
\IEEEauthorblockA{\textit{Imperial College London}\\
London, UK \\
g.gorman@imperial.ac.uk}
}
